General purpose gene annotation using deep learning

### 2020-04-21 paper/main.tex
minor

We also used multiple techniques to improve the prediction quality after the training was done. One very effective way for genomes with larger genes was to input longer sequences during inference time than during training. This was done for all animal genomes except the invertebrates. The input sequences were up to 10 times larger, depending on species group and assembly quality. This also demonstrates the ability of our model to generalize as it is able to make successful prediction on far longer sequences than it has ever seen. The sequence length during inference can be any of 20.000, 50.000, 100.000 or 200.000 and is determined by the phylogenetic class. The assignment was chosen to keep the average gene length roughly proportional to the length of the sequence input. For more implementation details on this see Section \ref{sec:longer} or the source code.

>>>>

We also used multiple techniques to improve the prediction quality after the training was done. One very effective way for genomes with larger genes was to input longer sequences during inference time than during training. This was done for all animal genomes except the invertebrates. The input sequences were up to 10 times larger, depending on species group and assembly quality. This also demonstrates the ability of our model to generalize as it is able to make successful prediction on far longer sequences than it has ever seen. The sequence length during inference can be up to 200.000 base pairs long and is determined by the phylogenetic class. The concrete lengths were chosen to keep the average gene length roughly proportional to the length of the sequence input. For more implementation details on this see Section \ref{sec:longer} or the source code.
